Assesing Health Care Coverage and Access Utilizing the National Health Interview Survey

### 2017-03-06 paper/paper.Rmd
more on methods

# INTRODUCTION
Healthcare...(a hook, why we are doing it and then transition to three questions we have).

The Patient Protection and Affordable Care Act (PPACA), commonly shortened to the Affordable Care Act (ACA) and nicknamed Obamacare, is one of the most important healthcare legislature, creating a significant impact on the US Health care system. However, with the arrival of President Trump in the Oval Office, and with the ACA repeal now underway, some speculate huge consequences, such as increased death rates([@trump]).

@@

# METHODS
A detailed explanation of the techniques and algorithms you used to solve the problem.

@@

## Descriptive Statistics

## Plots

>>>>

# INTRODUCTION
The Patient Protection and Affordable Care Act (PPACA), commonly shortened to the Affordable Care Act (ACA) and nicknamed Obamacare, is one of the most important healthcare legislature, creating a significant impact on the US Health care system. However, with the arrival of President Trump in the Oval Office, and with the ACA repeal now underway, some speculate huge consequences such as increased death rates([@trump]). In light of these recent events, it is important that we take a look at the current state of our healthcare system and question whether it is failing or not.

@@

# METHODOLOGY
To answer the questions we layed out, we use data provided from the NHIS survey. We used various subsets of the survey data, depending on the specific question being analyzed.

## **Educational Attainment Vs Healthcare Access**

## **Health Care Access**

## **Health Care Expedentiture**
To gain a general outlook on the healthcare system, one way of looking at it is through the perspective of expenditures. Specifically the question we wanted to explore is, _"How has the amount of money spent for medical care changed over the years?"_ One specific variables that was counted for from the survey was **"Amount family spent for medical care, past 12 months"** (N = ). This variable only provided a rough estimate on the family's expenditure on medical care, but is still relevant since interviewers directed respondents to exclude the insurance premiums, over-the-counter drugs, and any costs for which they expected to be reimbursed. Using the provided calculated weight and strata, a **stratified random sampling** was implemented to calculate a weighted score.

@@

## **Plots**

### 2017-03-06 paper/paper.tex
more on methods

Healthcare\ldots{}(a hook, why we are doing it and then transition to
three questions we have).

The Patient Protection and Affordable Care Act (PPACA), commonly
shortened to the Affordable Care Act (ACA) and nicknamed Obamacare, is
one of the most important healthcare legislature, creating a significant
impact on the US Health care system. However, with the arrival of
President Trump in the Oval Office, and with the ACA repeal now
underway, some speculate huge consequences, such as increased death
rates(\citep{trump}).

@@

\section{METHODS}\label{methods}

A detailed explanation of the techniques and algorithms you used to
solve the problem.

@@

>>>>

The Patient Protection and Affordable Care Act (PPACA), commonly
shortened to the Affordable Care Act (ACA) and nicknamed Obamacare, is
one of the most important healthcare legislature, creating a significant
impact on the US Health care system. However, with the arrival of
President Trump in the Oval Office, and with the ACA repeal now
underway, some speculate huge consequences such as increased death
rates(\citep{trump}). In light of these recent events, it is important
that we take a look at the current state of our healthcare system and
question whether it is failing or not.

@@

\section{METHODOLOGY}\label{methodology}

To answer the questions we layed out, we use data provided from the NHIS
survey. We used various subsets of the survey data, depending on the
specific question being analyzed.

\subsection{\texorpdfstring{\textbf{Educational Attainment Vs Healthcare
Access}}{Educational Attainment Vs Healthcare Access}}\label{educational-attainment-vs-healthcare-access}

\subsection{\texorpdfstring{\textbf{Health Care
Access}}{Health Care Access}}\label{health-care-access}

\subsection{\texorpdfstring{\textbf{Health Care
Expedentiture}}{Health Care Expedentiture}}\label{health-care-expedentiture}

To gain a general outlook on the healthcare system, one way of looking
at it is through the perspective of expenditures. Specifically the
question we wanted to explore is, \emph{``How has the amount of money
spent for medical care changed over the years?''} One specific variables
that was counted for from the survey was \textbf{``Amount family spent
for medical care, past 12 months''} (N = ). This variable only provided
a rough estimate on the family's expenditure on medical care, but is
still relevant since interviewers directed respondents to exclude the
insurance premiums, over-the-counter drugs, and any costs for which they
expected to be reimbursed. Using the provided calculated weight and
strata, a \textbf{stratified random sampling} was implemented to
calculate a weighted score.

@@

\subsection{\texorpdfstring{\textbf{Plots}}{Plots}}\label{plots}
